### 2018-04-30 paper/global-overlay-design.tex
lala

\newcommand{\viewsize}{\ensuremath{l_{\text{view}}}}
\NewAlgorithm{\GetRandomPeer}{RPS()}

To reach this goal, we employ Random Peer Sampling (RPS) \cite{Voulgaris_Gavidia_van_Steen_2005,Jelasity_Voulgaris_Guerraoui_Kermarrec_van_Steen_2007}.
Essentially, each node maintains a \emph{view} containing \viewsize other devices' descriptors. 
By periodically exchanging random descriptors with a carefully selected node from its view, RPS allows devices to always have a fairly random sample of the nodes in the system inside their view.
Due to the RPS's eviction policy, stale descriptors are removed quickly: each device thus knows a random sample of \viewsize connected nodes.
An RPS descriptor for device $d$ is constituted of the following information:
\begin{itemize}
  \item Its address: $@_d$;
  \item Its public key: \(\pk_d\);
  \item Its probability of being online in the near future, as provided by the Squad Overlay: $p_d=P\left[d \in O_{t+1} | S_t\right]$.
\end{itemize}

Devices now have all the information they need to establish reliable PORs between two sets of devices.

>>>>

\newcommand{\viewsize}{\ensuremath{l_{\text{view}}\xspace}}
\newcommand{\view}{\ensuremath{\mathcal{V}_{\text{RPS}}\xspace}}
\NewAlgorithm{\GetRandomPeer}{random descriptor from \view}

To create PORs, devices need to know the address, encryption key, and probability of remaining available of some nodes in the system, to pick them as relays on the route.

To reach this goal, we employ Random Peer Sampling (RPS) \cite{Voulgaris_Gavidia_van_Steen_2005,Jelasity_Voulgaris_Guerraoui_Kermarrec_van_Steen_2007}.
Essentially, each node maintains a view \view containing \viewsize other devices' descriptors. 
This view is periodically updated as follows: a device $d$ pops the oldest descriptor $d'$ from its view, then swaps a predefined number of $l$ elements from \view with $d'$.
Both devices add a descriptor for themselves to the view exchange.
If $d'$ was offline, its descriptor is simply removed from the $d$'s view, but \view is otherwise not updated.

This allows for two things: firstly, each device's view contains a constantly changing random sample of the whole set of devices;
secondly, offline nodes get removed from one's view fairly fast---we can say that a \view contains \emph{mostly} descriptors of online devices.

In \name, an RPS descriptor for device $d$ is constituted of the following information:
\begin{itemize}
  \item Its address: $d$;
  \item Its public key: \(\pk_d\);
  \item Its probability of being online in the near future, as provided by the Squad Overlay: $p_d=P\left[d \in O_{t+1} | S_t\right]$.
\end{itemize}

Devices now have all the information they need to establish reliable PORs.

### 2018-04-30 paper/squad-overlay-design.tex
lala

We show in section~\label{sub:predictive_onion_routes_creation} that the prediction of their availability at $t+1$ is a good enough estimator of their connection state at $t+i$.
For that reason, devices only share $P\left[ d \in O_{t+1} \mid S_{t} = s \right]$ with other devices for PORs creation.

>>>>

We show in section~\ref{sub:predictive_onion_routes_creation} that the prediction of devices' availability at $t+1$ is a good enough estimator of their connection state at $t+i$.
For that reason, devices only compute and publish $P\left[ d \in O_{t+1} \mid S_{t} = s \right]$.
